---
title: "p8105_hw5_dcm2192"
author: "Dylan Morgan"
date: "2024-11-15"
output: github_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(rvest)
set.seed(1)
```

### Problem 1


### Problem 2

Define function.
```{r}
sim_mean_sd <- function(mu, n = 30, sigma = 5) {
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma)
  )
  sim_data |> 
    t.test() |> 
    broom::tidy() |> 
    summarize(
      mu_hat = estimate, 
      p_value = p.value
    )
}
```

Datasets with mu 0-6.
```{r}
sim_results_df <- 
  expand_grid(
    mu = c(0:6),
    iter = 1:5000
  ) |> 
  mutate(
    estimate_df = map(mu, sim_mean_sd)
  ) |> 
  unnest(estimate_df)

head(sim_results_df, 10)
```

Plot mu 0-6 where null was rejected. 
```{r}
sim_results_df |> 
  filter(p_value <= 0.05) |> 
  group_by(mu) |> 
  summarize(n_obs = n()) |> 
  ggplot(aes(x = mu, y = n_obs)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "True value of mu", y = "Number of times null was rejected")
```

The relationship between effect size and power is such that the number of times the null is rejected increases as the true value of mu increases. 

Plot avg estimate of mu-hat and true value of mu. 
```{r}
sim_results_df |> 
  group_by(mu) |> 
  summarize(avg_mu_hat = mean(mu_hat)) |> 
  ggplot(aes(x = mu, y = avg_mu_hat)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "True value of mu", y = "Average estimate of mu-hat")
```

Plot avg estimate of mu-hat (where null was rejected) and true value of mu. 
```{r}
sim_results_df |> 
  filter(p_value <= 0.05) |> 
  group_by(mu) |> 
  summarize(avg_mu_hat = mean(mu_hat)) |> 
  ggplot(aes(x = mu, y = avg_mu_hat)) + 
  geom_point() + 
  geom_line() + 
  labs(x = "True value of mu", y = "Average estimate of mu-hat where null was rejected")
```

The sample average of mu-hat across tests for which the null is rejected is approximately equal to the true value of mu because for mu values greater than 3, the average mu-hat estimate is virtually equal to the true value of mu. This is not the case for the average mu-hat estimates for the mu values of 1 and 2, respectively; as the true value of mu increases from 1, however, the average mu-hat estimate gets closer to the true value of mu. 

### Problem 3

Load raw data.  
```{r}
homicide_data <- 
  read_csv("./data/homicide-data.csv")
```

The raw data for `homicide_data` contains `r nrow(homicide_data)` observations of `r ncol(homicide_data)` variables. The variables featured in this dataset include the reported date of the homicide; the name, race, age, and sex of the victim; the location in which the homicide occurred; and the status of the case (`disposition`) in terms of whether it remains open with no arrest, or whether it has been closed with or without an arrest. 

Create city_state variable, summarize homicide data by city_state.
```{r}
homicide_data <-
  homicide_data |>
  mutate(
    city_state = str_c(city, ", ", state)
  )

homicide_data |>
  group_by(city_state) |>
  summarize(n_obs = n())

homicide_data |> 
  filter(disposition != "Closed by arrest") |> 
  group_by(city_state, disposition) |> 
  summarize(n_obs = n())
```

Baltimore prop test.
```{r}
baltimore_prop_test <- 
  prop.test(
  x = (homicide_data |> 
         filter(city_state == "Baltimore, MD", 
                disposition != "Closed by arrest") |> 
         nrow()), 
  n = (homicide_data |> 
         filter(city_state == "Baltimore, MD") |> 
         nrow()), 
  p = 0.5) |> 
  broom::tidy() |> 
  select(estimate, conf.low, conf.high) |> 
  mutate(
    city_state = "Baltimore, MD"
  ) |> 
  relocate(city_state, .before = estimate)

baltimore_prop_test
```

Define prop test function to apply to all city_state values.
```{r}
prop_test_func <- function(city_state_param) {
  prop.test(
    x = (homicide_data |> 
           filter(city_state == city_state_param, 
                  disposition != "Closed by arrest") |> 
           nrow()), 
    n = (homicide_data |> 
           filter(city_state == city_state_param) |> 
           nrow()), 
    p = 0.5) |> 
    broom::tidy() |> 
    select(estimate, conf.low, conf.high)
}
```

Map through city_state in homicide data.
```{r}
prop_test_results_df <- 
  expand_grid(
    city_state = unique(homicide_data$city_state)
  ) |> 
  mutate(
    prop_est_df = map(city_state, prop_test_func)
  ) |> 
  unnest(prop_est_df)

head(prop_test_results_df, 10)
```

Plot prop estimates of unsolved homicides and CIs for each city.
```{r}
prop_test_results_df |> 
  ggplot(aes(x = fct_rev(fct_reorder(city_state, estimate)))) + 
  geom_col(aes(y = estimate)) + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text = element_text(angle = 90)) + 
  labs(x = "City", y = "Estimated Proportion of Unsolved Homicides")
```




